---
title: "Multiple Integration Tool Check - Issues"
output: html_document
params:
  gVars: NA
  input: NA
  srcDir: NA
always_allow_html: yes
---

<br>
<style>
body {
text-align: justify}
</style>

## Integration of Multiple Curated Datasets

## Timestamp 
```{r, echo=FALSE}

print(Sys.time())

```
<br>


## Session Unique Identifier
```{r, echo=FALSE}
id <- data.frame(params$gVars$sha256_stringID)
kbl(id, format="html",booktabs = TRUE, align="c",
                col.names = NULL, table.attr = "style = \"color: dodgerblue;\"")  %>% 
                     kable_styling (font_size = 16, bootstrap_options = c("striped", "condensed")) %>%
  column_spec(1, bold=TRUE)

```
<br>

## Arbiter(s) evaluating the entries as 'Issues'
```{r, echo=FALSE , results='asis'}

if (length(params$gVars$multi_ISSmsg)>0){
  
      arbiterISS <- purrr::map(params$gVars$multi_ISSmsg,2)  %>% as.character(.)%>% unique(.) 
      } else { arbiterISS<-"NA"}

if (length(params$gVars$multi_ISSmsg)>0){
  arbiterISS_kbl <- kbl(arbiterISS, escape = FALSE, format="html", booktabs = TRUE, align=c("l","c"),
                     col.names=NULL, row.names=TRUE) %>%
                    kable_styling(bootstrap_options = c("striped", "condensed")) %>% column_spec(1, width = "30em")
                     
  cat(arbiterISS_kbl) 
  } else {cat("No entries assessed as 'Issues'")} 

```



## List of the 'Issue' entries to re-evaluate
<div align="justify">
Each block reports the tracking ID to link easily the correspondent step in the procedural report. 
If absent, the missing IDs referred to a misclassified entry, operation later undone. <br>
Below the ID, it is indicated the column name, the correspondent files and the entries contained in the file but not in the vocabulary. <br>
In the remote case, where all the entries were already present in the vocabulary, but the user finds and mark as "Issue" some inconsistency, the reporting block is slightly modified. The report is enriched by an explanatory note and the block lists only the filenames and not all the entries. <br>
The messages are an extended version of those in the Procedures/GLP report, were the contents associated to the file name are not indicated.
</div>



```{r, echo=FALSE, results= 'asis'}

if (length(params$gVars$multi_ISSmsg)>0){
  all_issues <- as.data.frame(params$gVars$multi_ISSmsg) %>% 
                        do.call(rbind.data.frame, .)  %>% setNames(.,c("Entries to review", "Arbiter")) #%>%      head(.)
  issues_kbl <- kbl(all_issues, escape = FALSE, format="html", booktabs = TRUE, align=c("l","c"),
                     col.names=c("Entries to review", "Arbiter"), row.names=FALSE) %>%
                    kable_styling(bootstrap_options = c("striped", "condensed"))
                     
  cat(issues_kbl) 
  }

```

